---
title: "EDA"
author: "Melody Jiang"
date: "1/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
set.seed(42)
```

```{r}
df <- read.csv("AB_NYC_2019.csv")
```

```{r}
str(df)
```

```{r}
head(df)
```

```{r}
summary(df)
```

# Thoughts and observations

How do we characterize popularity? num_of_reviews, last_review, reviews_per_month, availability.

The problem with reviews per month might be it is not popular initially and that dilutes stuffs. Maybe take something like number_of_reviews / reviews_per_month gives us how long the listing have been having reviews - how long this listing have been "open". Maybe use this and take out number_of_reviews.

It is also possible that people rent but doesn't leave review. availability_365 & minimum_nights might give a sense of number of visits. However, what's the interpretation of availability_365? Number of unbooked days in 2019? Seems a better characterization of "popularity" than traffic, since I charge by days.

Reviews might boost my popularity, so do consider that. Maybe as an aspect to include but not putting too much emphasize on it for our goal.

Price is in price per night right?

To characterize our desired goal, we might want to maximize total profit, taking both popularity and price into account. 

Aspects of naming - length, diction. Maybe just eyeball and find pattern for top listings.









