---
title: "EDA 4"
author: "Melody Jiang"
date: "1/31/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(reshape)
library(ggplot2)
library(broom)
library(corrplot)

library(ggmap)
library(maps)
library(mapdata)
library(geojsonio) # to read geojson files
library(ggthemes)
library(sf)
```

# Justification of long vs short stay

```{r}
plt_length_stay <- ggplot(data = d_clean, aes(x = minimum_nights)) + 
  geom_density() +
  geom_vline(xintercept=30, color = "red", size = 0.3) +
  scale_x_continuous(breaks=c(0, 30, 100, 200, 300))
plt_length_stay
ggsave("length_stay_density.jpeg", path = "Deliverables/Figures", width = 5, height = 3.5)
```

```{r}
ggplot(data = d_clean, aes(x = type_stay, y = price_log)) +
  geom_boxplot()
  
```

```{r}
ggplot(data = d_clean, aes(x = type_stay, y = log(popularity))) +
  geom_boxplot()
```

```{r}
df_short <- d_clean[d_clean$type_stay == "Short", ]
```

# Justification of created variables

## proximity_metro

```{r}
plt_log_price_vs_prox_metro <- ggplot(data = d_clean, aes(x = proximity_metro, y = price_log)) +
  geom_point()
plt_log_price_vs_prox_metro
``` 

```{r}
ggplot(data = df_short, aes(x = proximity_metro, y = price_log)) +
  geom_point()
```

```{r}
plt_popularity_vs_prox_metro <- ggplot(data = d_clean, aes(x = proximity_metro, y = popularity )) +
  geom_point()
plt_popularity_vs_prox_metro
```

```{r}
plt_log_popularity_vs_prox_metro <- ggplot(data = d_clean, aes(x = proximity_metro, y = log(popularity) ), size = 0.1) +
  geom_point()
plt_log_popularity_vs_prox_metro
```

```{r}
ggplot(data = df_short, aes(x = proximity_metro, y = popularity)) +
  geom_point()
```

```{r}
plt_review_vs_prox_metro <- ggplot(data = d_clean, aes(x = proximity_metro, y = reviews_per_month)) +
  geom_point()
plt_review_vs_prox_metro
```

```{r}
ggplot(data = df_short, aes(x = proximity_metro, y = log(reviews_per_month) )) +
  geom_point()
```

## proximity_attraction
 
```{r}
plt_log_price_vs_prox_attr <- ggplot(data = d_clean, aes(x = proximity_attraction, y = price_log)) +
  geom_point()
plt_log_price_vs_prox_attr
```

```{r}
plt_popularity_vs_prox_attr <- ggplot(data = d_clean, aes(x = proximity_attraction, y = log(popularity) )) +
  geom_point()
plt_popularity_vs_prox_attr
``` 

```{r}
plt_review_vs_prox_attr <- ggplot(data = d_clean, aes(x = proximity_attraction, y = reviews_per_month)) +
  geom_point()
plt_review_vs_prox_attr
``` 

## name_host_freq

```{r}
plt_log_price_vs_name_freq <- ggplot(data = d_clean, aes(x = name_host_freq, y = price_log)) +
  geom_point()
plt_log_price_vs_name_freq
```

```{r}
plt_popularity_vs_name_freq <- ggplot(data = d_clean, aes(x = name_host_freq, y = popularity)) +
  geom_point()
plt_popularity_vs_name_freq
``` 

```{r}
plt_review_vs_name_freq <- ggplot(data = d_clean, aes(x = name_host_freq, y = reviews_per_month)) +
  geom_point()
plt_review_vs_name_freq
``` 

## name_host_special

```{r}
plt_log_price_vs_name_spec <- ggplot(data = d_clean, aes(x = name_host_special, y = price_log, fill = name_host_special)) +
  geom_boxplot()
plt_log_price_vs_name_spec
```

```{r}
plt_popularity_vs_name_spec <- ggplot(data = d_clean, aes(x = name_host_special, y = price_log, fill = name_host_special)) +
  geom_boxplot()
plt_popularity_vs_name_spec
```

```{r}
plt_review_vs_name_spec <- ggplot(data = d_clean, aes(x = name_host_special, y = reviews_per_month, fill = name_host_special)) +
  geom_boxplot()
plt_review_vs_name_spec
```

# Distribution of log price and log popularity

```{r}
hist(d_clean$price_log)
hist(log(na.omit(d_clean$popularity)))
```

# Map justification of including metro

```{r}
metro_loc <- read.csv("subway and attrctions data/subway_loc.csv")
```

```{r}
# This does not work.

# spdf <- geojson_read("nybb.shp",  what = "sp") # execute this in console
# 
# spdf_fortified <- fortify(spdf)
# 
# ny_base <- ggplot(data = spdf_fortified, mapping = aes(x = long, y = lat, group = group)) + 
#   coord_fixed(1.3) + 
#   geom_polygon(color = "black", fill = "gray")
# 
# ny_base
# 
# # try other way
# 
# ny_base_2 <- ggplot()
# ny_base_2 <- ny_base_2 + geom_map(data=spdf_fortified, map=spdf_fortified,
#                     aes(x=long, y=lat, map_id=id),
#                     color="black", fill="white", size=0.25)
# 
# ny_base_2 <- ny_base_2 + coord_equal() 
# #ny_base_2 <- ny_base_2 + theme_map()
# ny_base_2
# 
# # one way
# 
# ny_bro <- ny_base + 
#   geom_polygon(data = spdf_fortified, fill = NA, color = "white") +
#   geom_polygon(color = "black", fill = NA)  # get the state border back on top
# 
# map_metro <- ny_bro +
#   geom_point(data = metro_loc, mapping = aes(x = Station.Longitude, y = Station.Latitude))
# map_metro
# 
# 
# # adding metro - try the other way
# map_metro_2 <- ny_base_2 +
#   geom_point(data = metro_loc, mapping = aes(x = Station.Longitude, y = Station.Latitude))
# map_metro_2

``` 


```{r}

metro_loc <- metro_loc %>% mutate(color = rep("metro", times = nrow(metro_loc)))

ggplot()+
  theme_dark() +
  geom_point(data = d_clean[d_clean$price != 0, ], aes(x = longitude, y = latitude, color = price_log), size = 0.7)+
  scale_color_gradient2(midpoint = 4) +
  # scale_color_gradientn(colours = rainbow(7)) +
  geom_point(data = metro_loc, mapping = aes(x = Station.Longitude, y = Station.Latitude, shape = factor(color)), size = 0.7, color = "orange") +
  labs(shape = "")
 # coord_cartesian(xlim = c(-73.95, -73.9),ylim = c(40.6, 40.7))
```

```{r}
ggplot()+
  theme_dark() +
  geom_point(data = d_clean[d_clean$popularity != 0, ], aes(x = longitude, y = latitude, color = log(popularity)), size = 0.7)+
   scale_color_gradient2(midpoint = -3) +
#  scale_color_gradientn(colours = rainbow(7)) +
  geom_point(data = metro_loc, mapping = aes(x = Station.Longitude, y = Station.Latitude, shape = factor(color)), size = 0.7, color = "orange") +
  labs(shape = "")
#  coord_cartesian(xlim = c(-74.0, -73.9),ylim = c(40.6, 40.7))
```

# Map justification of including attractions

```{r}
df_attr_loc <- read.csv("subway and attractions data/attrac_loc.csv") # run in console
```

```{r}
ggplot()+
  theme_dark() +
  geom_point(data = d_clean[d_clean$price != 0, ], aes(x = longitude, y = latitude, color = price_log))+
    scale_color_gradient2(midpoint = 4) +
#  scale_color_gradientn(colours = rainbow(7)) +
    geom_point(data = df_attr_loc, mapping = aes(x = longitude, y = latitude), color = "orange") +
  coord_cartesian(xlim = c(-74.05, -73.95),ylim = c(40.7, 40.8))
```

```{r}
ggplot()+
  theme_dark() +
  geom_point(data = d_clean[d_clean$price != 0, ], aes(x = longitude, y = latitude, color = price_log), size = 0.8)+
    scale_color_gradient2(midpoint = 4.5) +
#  scale_color_gradientn(colours = rainbow(7)) +
    geom_point(data = df_attr_loc, mapping = aes(x = longitude, y = latitude, shape = factor(color)), color = "orange") +
  labs(shape = "")
#  coord_cartesian(xlim = c(-74.0, -73.9),ylim = c(40.6, 40.7))
```

```{r}
ggplot()+
  theme_dark() +
  geom_point(data = d_clean[d_clean$price != 0, ], aes(x = longitude, y = latitude, color = price_log), size = 0.7)+
    scale_color_gradient2(midpoint = 4) +
#  scale_color_gradientn(colours = rainbow(7)) +
    geom_point(data = df_attr_loc, mapping = aes(x = longitude, y = latitude), color = "orange")
```

```{r}



ggplot()+
  geom_point(data = d_clean[d_clean$popularity != 0, ], aes(x = longitude, y = latitude, color = log(popularity)), size = 0.5)+
  scale_color_gradient2(midpoint = -3.5) +
  geom_point(data = df_attr_loc, mapping = aes(x = longitude, y = latitude), size = 0.5)  
#  coord_cartesian(xlim = c(-74.0, -73.9),ylim = c(40.6, 40.7))
```

# Questiones

* Are we still using popularity
* We should remove those with price 0s
* problem with including attraction: some attrction takes up a lot of space! Attraction where it is impossible to have houses!
* name_host_freq doesn't seem to exhibit much
























